---
title: "The Evidence Synthesis 'Ecosystem'"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(scales)
library(bubbles)
library(RColorBrewer)
library(tidyverse)
library(kableExtra)
```

```{r read in and rduce lens data, echo=FALSE, warning=FALSE, message=FALSE}
Lens_dat <- readRDS(paste0(here::here(), "/data/Lens_dat.RDS"))
Lens_dat=Lens_dat %>% 
  janitor::clean_names() %>% 
  arrange(.,desc(document_count)) %>% 
  rowid_to_column() %>%
  mutate(percent=(document_count/sum(document_count)*100)) %>% 
  filter(percent>0.2)
```


```{r lens bubbleplot reduced, echo=FALSE, message=FALSE, warning=FALSE}
lens_bub=bubbles(
 Lens_dat$document_count,
 #label=NA,
 label=abbreviate(Lens_dat$field_of_study),
   tooltip = paste0(Lens_dat$field_of_study, " articles: ", Lens_dat$document_count),
  color = col_factor(
    brewer.pal(9,"Set1"),
    factor(Lens_dat$field_of_study)
  )(Lens_dat$field_of_study),
  height = 800,
  width = 800
)
lens_bub
# p <- '
# library(scales)
# library(bubbles)
# library(RColorBrewer)
# bubbles(
#    Lens_dat$document_count,
#   label=abbreviate(Lens_dat$field_of_study),
#    tooltip = paste0(Lens_dat$field_of_study, " articles: ", Lens_dat$document_count),
#   color = col_factor(
#     brewer.pal(9,"Set1"),
#     factor(Lens_dat$field_of_study)
#   )(Lens_dat$field_of_study),
#   height = 800,
#   width = 800
# )
# 
# '
#htmlwidgets::saveWidget(lens_bub, file=paste0(here::here(),"/html.widgets/lens_bub.html"))
# rbokeh::widget2gist(p, name = "ES bubbles Lens")
```
Articles in each "Field of Study" category returned from a search on lens.org for "Evidence synthesis OR Evidence based". Each bubble in the plot indicates a "Field of Study" (listed in the table below; hover your mouse over a bubble on the html version to see its label) with size relative to the proportion of the total 2792068 articles within that "Field of Study". Only the top `r dim(Lens_dat)[1] ` categories are included in the plot.

```{r legend reduced, echo=FALSE}
Lens_dat %>% 
  select(#rowid,
    field_of_study, document_count) %>% 
  mutate("Abbreviation"=abbreviate(field_of_study)) %>% 
  #rename("Label"=rowid) %>% 
  rename("Field of study"=field_of_study) %>% 
  rename("Number of articles"= document_count) %>% 
  
  #htmlTable(rnames = FALSE)
kableExtra::kbl() %>% 
  kableExtra::kable_paper() %>%
  kableExtra::scroll_box(width = "500px", height = "200px") #%>% 
  #kableExtra::save_kable(file = "table1.html", self_contained = T)
```